TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems

### 2017-02-11 ISORC2017/paper.tex
Fix system model by enago

This section describes the system model of TINET+TECS, including the basic technologies such as TINET and TECS.
System model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack, and the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
Moreover, TECS adapter supports the legacy codes for existing TCP/IP applications.

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
TINET has been released as open source.

To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

\begin{itemize}
    \item Minimum copy frequency
    \item Elimination of dynamic memory control
    \item Asynchronous interface
    \item Error detailed per API
\end{itemize}

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.

Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.

A TCP reception point called Reception Point (REP) is prepared to wait for a connection request from the partner side.
An REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes, and performs functions like {\it bind()} and {\it listen()}.

In TINET, the number of the data copy between each protocol layers is minimized.
A TCP/IP protocol stack for general computers has large overheads of execution time and memory consumption because the data is copied at each protocol layers.
To solve the problem, TINET does pass the pointer of the data buffer between each protocol layers, not perform data copy.

@@

TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs owing to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

In TECS, component deployment and composition are performed statically.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
    \caption{Component Diagram}
    \label{fig:ComponentDiagram}
\end{figure}

\subsubsection{Component Model}

Fig. \ref{fig:ComponentDiagram} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

\subsubsection{Component Description}

In TECS, components are described with component description language (CDL).
CDL can be divided into three categories: {\it signature}, {\it celltype}, and build description.
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sIPv4Output (Fig. \ref{src:signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in], [out], and [inout] are used, which represent input, output, and input/output respectively.
        [size\_is({\it len})] represents an array of size {\it len}.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description}
\label{src:signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sIPv4Output, and an {\it entry} port name, e.g., eIPv4Output, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;

@@

    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\caption{Celltype description}
\label{src:celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig. \ref{src:build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
        In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
        {\it C\_EXP} calls macros defined in C files.

>>>>

This section describes the system model of TINET+TECS, including basic technologies such as TINET and TECS.
A system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
TINET+TECS is a component-based TCP/IP protocol stack in which the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings using the TECS method.
Moreover, the TECS adapter supports the legacy codes for existing TCP/IP applications.

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
TINET has been released as an open-source tool.

To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the following functions:

\begin{itemize}
    \item minimum copy frequency,
    \item elimination of dynamic memory control,
    \item asynchronous interfacing,
    \item error detailing per API.
\end{itemize}

@@

TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, a real-time kernel based on $\mu$ITRON \cite{par:microITRON}.
As it is compatible with TOPPERS RTOS, TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP.

Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
Users transmit and receive data using a Communication End Point (CEP), an interface that functions like a socket.
In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.

A TCP reception point called the REP stands by to receive connection requests from the partner side.
The REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes and performs functions such {\it bind()} and {\it listen()}.

In TINET, the amount of data copying between each protocol layers is minimized.
In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
To solve this problem, TINET does passes the pointer of the data buffer between each protocol layer instead of performing data copying.

@@

TECS is a component system suitable for embedded systems that can increase productivity and reduce development costs based on the improved reusability of software components.
TECS also provides component diagrams that can help developers visualize the overall structure of a system.

In TECS, component deployment and composition are performed statically, and as a consequently, component connection does not incur significant overhead, and memory requirements can be reduced.
TECS has various features such as source level portability and fine-grained components and can be implemented in C.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
    \caption{Component diagram}
    \label{fig:ComponentDiagram}
\end{figure}

\subsubsection{Component model}

Fig. \ref{fig:ComponentDiagram} shows a component diagram.
{\it Cells}, which are instance of components in TECS, consist of {\it entry} ports, {\it call} ports, attributes, and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cells}, whereas a {\it call} port is an interface that enables the use of other {\it cells}' functions.
Each {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions that defines the interface definition of the {\it cell}.
The {\it cell's} {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

\subsubsection{Component description}

In TECS, components are described using component description language (CDL).
CDL can be divided into three categories: {\it signature}, {\it celltype}, and build description.
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s''--for instance, sIPv4Output (Fig. \ref{src:signature}).
        To clarify the function of an interface, specifiers such as [in], [out], and [inout] are used in TECS to represent the input, output, and input/output, respectively.
        Similarly, [size\_is({\it len})] represents an array of size {\it len}.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sIPv4Output {
  T_IN4_ADDR getIPv4Address(void);
  ER         getOffset([inout]T_OFF_BUF *offset);
  ER         setHeader([inout,size_is(size)]
                        int8_t *outputp,
                        [in]int32_t size,
                        [in]T_IN4_ADDR dstaddr,
                        [in]T_IN4_ADDR srcaddr);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description}
\label{src:signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines the {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sIPv4Output, and an {\it entry} port name, e.g., eIPv4Output, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tIPv4Output {
    /* Entry port */
    entry sIPv4Output eOutput;

@@

    attr {  /* Attribute */
        uint16_t fragInit = 0;
    };
    var {   /* Variable */
        uint16_t fragId = fragInit;
    };
};
\end{lstlisting}
\caption{Celltype description}
\label{src:celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig. \ref{src:build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
        In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
        {\it C\_EXP} can be used to call macros defined in C files.
